\documentclass[a4paper,english,thesis]{dcsbook}

\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{subfig}
\usepackage{appendix}
\usepackage{babel}

\usepackage{multirow}

\usepackage{pstricks}
\usepackage{psfrag}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathmorphing,backgrounds,positioning,fit}

\usepackage{algorithm}
\usepackage{algpseudocode}

\renewcommand{\appendixtocname}{Appendices}
\renewcommand{\appendixpagename}{Appendices}

\author{Igor~Kupczy\'nski}
\university{Pozna\'n University of Technology}
\supervisor{prof. dr hab. in\.{z}. Roman~S\l{}owi\'nski}
\date{Pozna\'n 2010}

\title{Interactive Evolutionary Algorithm \\ for Robust Multi-Objective
  Optimization}

\input{z_tikz_styles}

\begin{document}
\maketitle
\frontmatter

\parbox{1cm}{
\vspace{15cm}
}

Writing the master's thesis was a~tremendous task, impossible to complete
without the support I~have received. I would like to thank my supervisor,
prof. Roman~S\l{}owi\'nski, for his help, reviews and encouragement.

I~have spent one semester at Universit\'{e} Paris-Dauphine. The discussions
with prof. Daniel Vanderpooten and his colleagues from LAMSADE\footnote{The
  LAMSADE laboratory, established in 1974, is the joint laboratory of
  Universit\'{e} Paris-Dauphine and CNRS (National Center for Scientific
  Research). Its central research activity lies at the interface of two
  fundamental scientific areas: Computer Science and Decision Making.} were
inspiring and as horizon-widening as the aura of the City of Light. I would
like to thank him for the opportunity.

Finally, I would like to thank one person I cannot name, the dedicated and
gifted linguist, for her inestimable comments.

\tableofcontents{}
\mainmatter

\chapter{Introduction}
\input{sec_introduction}
\chapter{Multi-Objective Optimization}
\input{sec_mmo}

\chapter{DARWIN, the Idea behind the Method}
\label{darwin-the-idea}
\input{sec_darwin_idea}
\chapter{Implementation of DARWIN}
\label{darwin-implementation}
\input{sec_implementation}

\chapter{Results of Computational Experiments}
\label{exp-results}
\input{sec_experiment_results}

\chapter{Summary}
\input{sec_summary}

\backmatter \bibliographystyle{acm}
\bibliography{bibliography}

\appendix
\appendixpage
\addappheadtotoc
\input{app_user_manual}


\end{document}